Covariate analysis of ROSMAP Reprocessed RNASeq (with SVA)

### 2016-05-30 code/Rmd/ROSMAP_RNASeq_SVA_Reprocessed.Rmd
Changed SVA method to two-step in ROSMAP reprocessed rnaseq analysis

---
title: "Covariate analysis of ROSMAP Reprocessed RNASeq (with SVA)"
author: "Thanneer Perumal"
date: "`r date()`"
output: html_document
---
```{r knit2synapse, eval=FALSE}
library(knitr)
library(knit2synapse)
library(synapseClient)

@@

SURR.VAR = sva(VOOM.ADJUSTED.GENE_EXPRESSION$E, MODEL1, MODEL0, method = "irw", n.sv = NUM.SV, B = 20)$sv
colnames(SURR.VAR) = paste0('SV',1:dim(SURR.VAR)[2])

@@

p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC)) + geom_point() + xlim(c(-1,1))
p = p + geom_hline(yintercept = -log10(0.05), color = 'red') 
p = p + geom_vline(xintercept = log2(1.2), color = 'red') 
p = p + geom_vline(xintercept = -log2(1.2), color = 'red') + facet_grid(.~Comparison, scales = 'fixed')
p
```
### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = "ROSMAP RNASeq Reprocessed Counts (Based on cogdx)", parentId = parentId)
CODE <- synStore(CODE)

>>>>

---
title: "Covariate analysis of ROSMAP Reprocessed RNASeq (with SVA)"
author: "Thanneer Perumal"
date: "`r date()`"
output: html_document
---
```{r knit2synapse, eval=FALSE}
library(knitr)
library(knit2synapse)
library(synapseClient)
library(githubr)

@@

SURR.VAR = sva(VOOM.ADJUSTED.GENE_EXPRESSION$E, MODEL1, MODEL0, method = "two-step", n.sv = NUM.SV, B = 30)$sv
colnames(SURR.VAR) = paste0('SV',1:dim(SURR.VAR)[2])

@@

p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC)) + geom_point() + xlim(c(-1,1))
p = p + geom_hline(yintercept = -log10(0.05), color = 'red') 
p = p + geom_vline(xintercept = log2(1.2), color = 'red') 
p = p + geom_vline(xintercept = -log2(1.2), color = 'red') + facet_grid(.~Comparison, scales = 'fixed')
p
```
### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = "ROSMAP RNASeq Reprocessed Counts (Based on cogdx with SVA)", parentId = parentId)
CODE <- synStore(CODE)
